---
title: "WordPress Agents Exploratory Analysis- Part I- Univariate description - Refactored"
author: "Viviane Schneider"
date: "08/01/2019"
output: html_document
---
**Type of Analysis:** Descriptive analysis - Univariate description

**Intention of Analysis**: 
1- Understand how Core WordPress Community coproduce code.
2- Identify potential indicators for coherence analysis.

**General Question:** *Wich are the atributes of coproduction (colunms of dataframe or variables)?*
**Specific Questions:** *Which type of developers groups exist in WC? It is possible to make some indicator from this data? *

**Source:** Data come from WordPress Report Trac System.
[URL Source](https://core.trac.wordpress.org/query?status=accepted&status=assigned&status=new&status=reopened&status=reviewing&col=id&col=summary&col=status&col=owner&col=type&col=priority&col=milestone&col=component&col=version&col=severity&col=resolution&col=time&col=changetime&col=focuses&col=reporter&col=keywords&order=priority)
**Dataframe:** [GitHub Repository](https://raw.githubusercontent.com/vivianesch/CoherenceAnalysisWordPress/master/TicketW.csv)

**Date collection:** 04/07/2019.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1.GENERAL ANALYSIS**

```{r}
#READ DATA
library(readr)
library(dplyr)
library(plotly)
library(tidyr)

TicketW <- read_csv('~/PhD Analysis/1. PhD escriptive exploratory analysis/TicketW.csv')
View(TicketW)
dim(TicketW) #dimension
TicketW[1:5,]  #5 fist lines
summary(TicketW)
glimpse(TicketW)

```


**Function unianalysis() - Transform vector into a data frame with frequency of levels and proportion**

```{r}
# Transform vector into a data frame with frequency of levels and proportion
.Unianalysis = function (x) {
    y <- as.data.frame(as.table(table(x)))
    y <- mutate(y, proportion = prop.table(y$Freq) *100)#Proportion
    y <- arrange(y, desc(y$Freq))
return(y)
}

```

**1.1 Variables related with members Analysis**
**Goal:** Find which variables have hight variability, and find a line of cut, in order to use into Bivariate Analysis.

```{r}

# Var1
Status<-.Unianalysis(TicketW$Status)

#Var2
TType<-.Unianalysis(TicketW$Type)

#Var3
Priority<-.Unianalysis(TicketW$Priority)

#Var4
Milestone<-.Unianalysis(TicketW$Milestone)

#Var5
Component<-.Unianalysis(TicketW$Component) 
Component = filter(Component, Freq>90) # Filter components with more than 100 tickets
sum(Component$Freq) #Total Tickets into most frequent components (more than 100 tickets)

#Var6
Severity<-.Unianalysis(TicketW$Severity)

#Var7
Focuses<-.Unianalysis(TicketW$Focuses)
Focuses = filter(Focuses, Freq>10) # Filter Focuses with more than 10 tickets
Focuses<-Focuses[order(Focuses$Freq, decreasing = TRUE),]
sum(Focuses$Freq) #Total Tickets into most frequent components (more than 100 tickets)

#Var8
Keywords<-.Unianalysis(TicketW$Keywords)
Keywords = filter(Keywords, Freq>8)
Keywords<-Keywords[order(Keywords$Freq, decreasing = TRUE),]
sum(Keywords$Freq)


```


**Functions for establish groups of active (GroupActive()), median (GroupMedian()), or less active (GroupAlien()) members: **

```{r}

#1. Filter Group of agents 
.Grouping = function(x, less, more) {
        y = filter(x, Freq < less & Freq > more)
        x <- y[order(y$Freq, decreasing = TRUE),]
        return(x)
}

```

**1.2 Variable Members Analysis - Reporters:** Reporters are WordPress Community members who find and report a problem from WP Platform, into a Ticket.

**Goal:** Find type of report member groups (actives, medians, and aliens), and find a line of cut, in order to use into Bivariate Analysis.
     
```{r}
#Find Groups and quantity of people for each group
             
Reporter<-.Unianalysis(TicketW$Reporter) 
totalReporter<-nrow(Reporter)

ActiveReporters<-.Grouping(Reporter, 1000, 10)
totalAR<-nrow(ActiveReporters)

MedianReporters<-.Grouping(Reporter, 10, 4)
totalMR<-nrow(MedianReporters)

LessReporters<-.Grouping(Reporter, 4, 0)
totalLR<-nrow(LessReporters)

```


**1.3 Variable Member Analysis - Owners:** Owners are WordPress Community members who pick up a ticket from WP Platform (sended by a reporter) in order to solve it.


**Goal:** Find type of owner member groups (actives, medians, and aliens), and find a line of cut, in order to use into Bivariate Analysis.
```{r}
Owner <-.Unianalysis(TicketW$Owner) 
totalOwner <-nrow(Owner)

#Find Groups and quantity of people for each group
             
ActiveOwner <-.Grouping(Owner, 1000, 10)
totalAO <-nrow(ActiveOwner)

MedianOwner <-.Grouping(Owner, 10, 4)
totalMO <-nrow(MedianOwner)

LessOwner <-.Grouping(Owner, 4, 0)
totalLO <-nrow(LessOwner)


```


**1.4 Sum of groups by Reporters and Owners:** 

```{r}
#Total members per Reporter
MembersTotal<-c(totalAR,totalMR,totalLR)
CoreGroup<-rbind("Active Reporters","Median Reporters","Alien Reporters")
WPCGroupR<-data.frame(CoreGroup,MembersTotal)

#Total members per Owner
MembersTotal<-c(totalAO,totalMO,totalLO)
CoreGroup<-rbind("Active Owners","Median Owners","Alien Owners")
WPCGroupO<-data.frame(CoreGroup,MembersTotal)

#Total members per every groups
MembersTotal<- c(totalOwner,totalReporter)
CoreGroup <- rbind("Owners","Reporters")
WPCGroups <- data.frame(CoreGroup,MembersTotal)


```


**2. DESCRIPTION ANALYSIS REPORT :** 

**2.1  Variables related with members Report:** Variables selected to bivariate analysis are Component(+100 tickets per level), Focuses (+1 Ticket per level), Keywords(+9 tickets per level), Type, Status.

```{r}
library(plotrix)
library(plotly)
library(ggplot2)
library(wordcloud)

#Graphic Function
#Fun Plot
.Plot_FunPlot = function(x,y) {
  fan.plot(x$Freq,
           max.span=pi,
           labels=paste(x$x, x$Freq, sep=": "),
            main=y,ticks=360)
}
#Word Plot
.Plot_word = function(x, num1, num2) {
     wordcloud(words = x$x, freq = x$Freq, min.freq = num1,
              max.words=num2, random.order=FALSE, rot.per=0.35, 
              colors=brewer.pal(8, "Dark2")) 
}

Status#Var1
#Graphics
.Plot_FunPlot(Status, "Tickets per Status")

TType# Var2
#Graphics
.Plot_FunPlot(TType, "Tickets per Type")

Priority# Var3
#Graphics
.Plot_FunPlot(Priority, "Tickets per Priority")

Milestone#Var4
#Graphics
.Plot_FunPlot(Milestone, "Tickets per Milestone")

Component#Var5
#Graphic
.Plot_FunPlot(Component, "Tickets per Component (more than 90 tickets)")

Severity #Var6
#Graphics
.Plot_FunPlot(Severity, "Tickets per Severity")

Focuses#Var7
#Graphics
pie(Focuses$Freq, main="Focuses", label = paste(Focuses$x, sep=": ", Focuses$Freq), col = rainbow(7))
.Plot_word(Focuses, 20, 200)

Keywords#Var8
#Graphics
pie(Keywords$Freq, main="Focuses", label = paste(Keywords$x, sep=": ", Keywords$Freq), col = rainbow(7))
.Plot_word(Keywords, 4, 300)

```



**2.2 Reporter Members Analysis Report** The groups of Reporters:

```{r}
ActiveReporters #Ranking the most active reporters
MedianReporters #Ranking the Median active reporters
LessReporters[c(1:30),c(1:2)] #Ranking the 30 less active Reporters

#Grafic of Top 5 active Reporters
.Plot_FunPlot(ActiveReporters[1:5, 1:2], "5 Top Active Reporters")
.Plot_FunPlot(MedianReporters[1:5, 1:2], "5 Top Median Reporters")
.Plot_FunPlot(LessReporters[1:5, 1:2], "5 Top Less Active Reporters")


```


**2.3 Owner Members Analysis Report:** The groups of Owners:

```{r}

ActiveOwner#Ranking the most active Owners
MedianOwner#Ranking the Median Owners
LessOwner[c(1:30),c(1:2)]#Ranking the 30 less active Owners

#Grafic of Owners

#Grafic of Top 5 active Owners
.Plot_FunPlot(ActiveOwner[1:5, 1:2], "5 Top Active Owners")
.Plot_FunPlot(MedianOwner[1:5, 1:2], "5 Top Median Owners")
.Plot_FunPlot(LessOwner[1:5, 1:2], "5 Top Less Active Owners")

```

**2.4 Comparation of groups by Reporters and Owners:**

```{r}
WPCGroups
par(mfrow=c(1,2))
barplot(WPCGroupR$MembersTotal,
        names.arg=WPCGroupR$MembersTotal,
        xlab="Reporter Groups",
        ylab="Total Members",
        legend=WPCGroupR$CoreGroup,
        col=rainbow(8),
        main="Reporters per Groups",border="red")

barplot(WPCGroupO$MembersTotal,
        names.arg=WPCGroupO$MembersTotal,
        xlab="Owners Groups",
        ylab="Total Members",
        legend=WPCGroupO$CoreGroup,
        col=rainbow(8),
        main="Owners per Groups",border="red")


```




```{r}
# Load ggplot2
library(ggplot2)
library(dplyr)
# library
library(treemap)

# treemap
.Tree_Map = function(x){
  group <- paste(x$CoreGroup, x$MembersTotal)
  value <- x$MembersTotal
  data <- data.frame(group,value)
     treemap(data,
            index="group",
            vSize="value",
            type="index")  
}


par(mfrow=c(1,3))
.Tree_Map(WPCGroups) #Total Owner and Reporters
.Tree_Map(WPCGroupO) #Groups of Owners 
.Tree_Map(WPCGroupR) #Groups of Reporters

```



**3. POTENTIAL INDICATORS:** 

* The "Sense of Unity" Dimension indicator: 
  *  Mode_Agents_Rules: In a scale from O to 1, this indicator represents the principals rules the WP members play in the community: active, median and alien. This unformal rules are observed into formal groups: owners and reporters. The Hypothesis is  that the Reporters Group and the Owners Group have a similar distribution of tickets per its the respectives sub groups(active, median, and alien).
  
Hypothesis: $PropMo = PropMR$

Means: percentual of tickets into any subgroups into Owner Groups are similar thand percentual of tickets into any subgroups into Reporter Groups

  Where 
    PropMo is the proportion of tickets per active, median, and alien groups of Owners, and
    PropMR is the proportion of tickets per active, median, and alien groups of Reporters.
    
Hypothesis test: 

```{r}

PropMR<-prop.table(WPCGroupR$MembersTotal)# Proportion
PropMO<-prop.table(WPCGroupO$MembersTotal)# Proportion

similarityOR<-ifelse(PropMO>PropMR,1-(PropMO-PropMR),1-(PropMR-PropMO))
similarityOR<-mean(similarityOR)
similarityOR

```

Thus, Mode_Agents_Rules indicator is = similarityOR. 

**4. FINAL CONCLUSIONS:** 

There are more Reporters than Owners. Maybe because to report a problem in the WorPress Platform is easear than fix a problem. There are a two members, who can been considers the super active menbers of WP Community: SergeyBiryukov and johnbillion. SergeyBiryukov (number 1 of owners) was reponsable to 67 tickets, and also he report 15 Tickets (23o position of reporters). johnbillion (number 1 of owners) reports 72 tickets, and also was responsable for 16 tickets (3o position of owners). 

The hypothesis test proof (result: 0.9772515) indicates that there are a strong coesion into formals groups of core: owners and reporters.

Despite the most of tickets have no owner, there are not so many urgent issues. Around 93% of tickets are classified as Severity "normal", and 97% are classified as Priority "Normal". 

According with this description, are recommended analyse in a bivariable description the folow variables:

* Variables for setup a referential of the community (The "Referentiality" Dimension): Documentation of values, general view and beiefs of community

* Variables for analyse the "Prescritivity" dimension: Analyse the community referential with  "Focuses" Variable, in order to verify if the members produced what they stablished into referential. 

* Variables for analyse the "Sense of Unity" dimension: "Keywords"  Variable, in order to verify the correlation with groups 

* Variables for analyse the  the "Receptivity" dimension: Groups of members, correlation between groups and Status, Type, Milestone variables


