---
title: "WordPress Agents Exploratory Analysis- Part I- Univariate description"
author: "Viviane Schneider"
date: "09/07/2019"
output: html_document
---
**Type of Analysis:** Descriptive analysis - Univariate description

**Intention of Analysis**: 
1- Understand how Core WordPress Community coproduce code.
2- Identify potential indicators for coherence analysis.

**General Question:** *Wich are the atributes of coproduction (colunms of dataframe or variables)?*
**Specific Questions:** *Which type of developers groups exist in WC? It is possible to make some indicator from this data? *

**Source:** Data come from WordPress Report Trac System.
[URL Source](https://core.trac.wordpress.org/query?status=accepted&status=assigned&status=new&status=reopened&status=reviewing&col=id&col=summary&col=status&col=owner&col=type&col=priority&col=milestone&col=component&col=version&col=severity&col=resolution&col=time&col=changetime&col=focuses&col=reporter&col=keywords&order=priority)
**Dataframe:** [GitHub Repository](https://raw.githubusercontent.com/vivianesch/CoherenceAnalysisWordPress/master/TicketW.csv)

**Date collection:** 04/07/2019.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1.GENERAL ANALYSIS**

```{r}
#READ DATA
library(readr)
library(dplyr)
library(plotly)
TicketW <- read_csv('~/PhD Analysis/1. PhD escriptive exploratory analysis/TicketW.csv')
View(TicketW)
dim(TicketW) #dimension
TicketW[1:5,]  #5 fist lines
summary(TicketW)
glimpse(TicketW)

```

**1.1 Variables related with members Analysis**
**Goal:** Find which variables have hight variability, and find a line of cut, in order to use into Bivariate Analysis.

```{r}
# Var1
Status<-table(TicketW$Status)
# Transform into table
Status<-as.data.frame(as.table(Status))

#Var2
TType<-table(TicketW$Type)
# Transform into table
TType<-as.data.frame(as.table(TType))

#Var3
Priority<-table(TicketW$Priority)
# Transform into table
Priority<-as.data.frame(as.table(Priority))

#Var4
Milestone<-table(TicketW$Milestone)
# Transform into table
Milestone<-as.data.frame(as.table(Milestone))

#Var5
Component<-table(TicketW$Component)
# Transform into table
Component<-as.data.frame(as.table(Component))
c1<-Component[order(Component$Freq, decreasing = TRUE),]
Component = filter(Component, Freq>100)#Var5
sum(Component$Freq)

#Var6
Severity<-table(TicketW$Severity)
# Transform into table
Severity<-as.data.frame(as.table(Severity))

#Var7
Focuses<-table(TicketW$Focuses)
# Transform into table
Focuses<-as.data.frame(as.table(Focuses))
f1<-Focuses[order(Focuses$Freq, decreasing = TRUE),]
Focuses = filter(Focuses, Freq>10)
sum(Focuses$Freq)

Keywords<-table(TicketW$Keywords)#Var8
# Transform into table
Keywords<-as.data.frame(as.table(Keywords))
k1<-Keywords[order(Keywords$Freq, decreasing = TRUE),]
Keywords = filter(Keywords, Freq>9)
Keywords = filter(Keywords, Freq>40)
sum(Keywords$Freq)

```


**1.2 Variable Members Analysis - Reporters:** Reporters are WordPress Community members who find and report a problem from WP Platform, into a Ticket.

**Goal:** Find type of report member groups (actives, medians, and aliens), and find a line of cut, in order to use into Bivariate Analysis.
```{r}

# Transform into table
Reporter<-table(TicketW$Reporter) 
Reporter<-as.data.frame(as.table(Reporter))
summary(Reporter)
totalReporter<-nrow(Reporter)

#1.2.1 Filter the most active group of reporters (Which reporter with more than 10 tickets)
ActiveReporters = filter(Reporter,Freq>10)
totalAR<-nrow(ActiveReporters) #Total members of active reporters group
RankAR <- ActiveReporters[order(ActiveReporters$Freq, decreasing = TRUE),]
summary(RankAR$Freq)

#1.2.2 Filter the median active group of reporters (Which reporter with less than 10 tickets and more than 4 tickets)
MedianReporters = filter(Reporter,Freq<10 & Freq>4)
totalMR<-nrow(MedianReporters)
#Ranking the Median active reporters
RankMR <- MedianReporters[order(MedianReporters$Freq, decreasing = TRUE),]

#1.2.3 Filter the less active group of Report (Which reporter with less than 10 tickets)
LessReporters = filter(Reporter,Freq<4)
totalLR<-nrow(LessReporters)
#Ranking the less active Reporters
Ranklr <- LessReporters[order(LessReporters$Freq, decreasing = TRUE),]

```


**1.3 Variable Member Analysis - Owners:** Owners are WordPress Community members who pick up a ticket from WP Platform (sended by a reporter) in order to solve it.


**Goal:** Find type of owner member groups (actives, medians, and aliens), and find a line of cut, in order to use into Bivariate Analysis.
```{r}
# Transform into table
Owner<-table(TicketW$Owner) 
Owner<-as.data.frame(as.table(Owner))
summary(Owner)
totalOwner<-nrow(Owner)

# 1.3.1 Filter the most active group of Owners (Which Owner with more than 10 tickets)
ActiveOwner = filter(Owner,Freq>10)
totalAO<-nrow(ActiveOwner)
#Ranking the most active Owners
RankAO <- ActiveOwner[order(ActiveOwner$Freq, decreasing = TRUE),]

#1.3.2 Filter the median active group of Owners (Which Owner with less than 10 tickets and more than 4 tickets)
MedianOwner = filter(Owner,Freq<10 & Freq>4)
totalMO<-nrow(MedianOwner)
#Ranking the Median Owners
RankMO <- MedianOwner[order(MedianOwner$Freq, decreasing = TRUE),]

#1.3.3 Filter the less active group of Owners (Which Owner with less than 10 tickets)
LessOwner = filter(Owner,Freq<4)
totalLO<-nrow(LessOwner)
#Ranking the less active Owners
RanklO <- LessOwner[order(LessOwner$Freq, decreasing = TRUE),]

```


**1.4 Sum of groups by Reporters and Owners:** 

```{r}
#Total members per Reporter
MembersTotalR<-c(totalReporter,totalAR,totalMR,totalLR)
CoreGroupR<-c("Reporters","Active Reporters","Median Reporters","Alien Reporters")
PropMR<-prop.table(MembersTotalR)# Proportion
WPCGroupR<-data.frame(CoreGroupR,MembersTotalR,PropMR)

#Total members per Owner
MembersTotalO<-c(totalOwner,totalAO,totalMO,totalLO)
CoreGroupO<-c("Owners","Active Owners","Median Owners","Alien Owners")
PropMO<-prop.table(MembersTotalR) #Proportion
WPCGroupO<-data.frame(CoreGroupO,MembersTotalO,PropMO)

```


**2. DESCRIPTION ANALYSIS REPORT :** 

**2.1  Variables related with members Report:** Variables selected to bivariate analysis are Component(+100 tickets per level), Focuses (+1 Ticket per level), Keywords(+9 tickets per level), Type, Status.

```{r}

Status#Var1
#Graphics
pie(Status$Freq, main="Frequency of Tickets Status", label=Status$Var1, col = rainbow(7))

TType# Var2
#Graphics
pie(TType$Freq, main="Frequency of Tickets Type", label=TType$Var1, col = rainbow(7))

Priority# Var3
#Graphics
pie(Priority$Freq, main="Frequency of Tickets Priority", label=Priority$Var1, col = rainbow(7))

Milestone#Var4
#Graphics
pie(Milestone$Freq, main="Frequency of Tickets Milestone", label=Milestone$Var1, col = rainbow(7))

Component#Var5
#Graphics
barplot(Component$Freq, 
        xlab = "Tickets", 
        ylab = "Components", 
        main="Frequency of Tickets Component", 
        col = rainbow(5),
        legend.text = Component$Var1,
        horiz=TRUE,
        args.legend = list("bottom", bty="n", cex = 1))

Severity #Var6
#Graphics
pie(Severity$Freq, main="Frequency of Tickets Severity", label=Severity$Var1, col = rainbow(7))

Focuses#Var7
#Graphics
barplot(Focuses$Freq, 
        xlab = "Tickets", 
        ylab = "Focuses", 
        main="Frequency of Tickets Focuses", 
        col = rainbow(13),
        legend.text = Focuses$Var1,
        horiz=TRUE,
       args.legend = list("bottom", bty="n", cex = 1))

Keywords#Var8
#Graphics
barplot(Keywords$Freq,
        xlab = "Tickets", 
        ylab = "Keywords", 
        main="Frequency of Tickets Keywords", 
        col = rainbow(13),
        legend.text = Keywords$Var1,
        horiz=TRUE,
        args.legend = list("bottom", bty="n", cex = 1))
```



**2.2 Reporter Members Analysis Report** The groups of Reporters:

```{r}
RankAR #Ranking the most active reporters
RankMR #Ranking the Median active reporters
Ranklr[c(1:30),c(1:2)] #Ranking the 30 less active Reporters

#Grafic of Top 5 active Reporters
par(mfrow=c(1,3))
barplot(RankAR$Freq[1:5],
        names.arg=RankAR$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per Reporter",
        ylab="Reporters",
        col=rainbow(5),
        main="Top 5 active Reporters",
        border="blue",
        legend.text = RankAR$Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.8))#Top 5 Active Reporters

barplot(RankMR$Freq[1:5],
        names.arg=RankMR$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per Reporter",
        ylab="Reporters",
        col=rainbow(5),
        main="Top 5 Median Reporters",
        border="blue",
        legend.text = RankMR $Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.7))#Top 5 Median Reporters

barplot(Ranklr$Freq[1:5],
        names.arg=Ranklr$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per Reporter",
        ylab="Reporters",
        col=rainbow(5),
        main="Top 5 Alien Reporters",
        border="blue",
        legend.text = Ranklr$Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.7))#Top 5 Less acctive Reporters

```


**2.3 Owner Members Analysis Report:** The groups of Owners:

```{r}

RankAO#Ranking the most active Owners
RankMO#Ranking the Median Owners
RanklO[c(1:30),c(1:2)]#Ranking the 30 less active Owners

#Grafic of Owners
par(mfrow=c(1,3))
barplot(RankAO$Freq[1:5],
        names.arg=RankAO$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per owner",
        ylab="Owners",
        col=rainbow(5),
        main="Top 5 active Owners",
        border="blue",
        legend.text = RankAO$Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.7))#Top 5 Active Owners

barplot(RankMO$Freq[1:5],
        names.arg=RankMO$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per owner",
        ylab="Owners",
        col=rainbow(5),
        main="Top 5 median Owners",
        border="blue",
        legend.text = RankMO$Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.7))#Top 5 Median Owners

barplot(RanklO$Freq[1:5],
        names.arg=RanklO$Var1[1:5],
        horiz=TRUE,
        xlab="Tickets per owner",
        ylab="Owners",
        col=rainbow(5),
        main="The 5 less active Owners",
        border="blue",
        legend.text = RanklO$Var1[1:5],
        args.legend = list("bottom", bty="n", cex = 0.7))#Top 5 Less Active Owners

```

**2.4 Comparation of groups by Reporters and Owners:**

```{r}
WPCGroupR #Group Types of Reporters
WPCGroupO #Group Types of Owners

par(mfrow=c(1,2))
barplot(WPCGroupR$MembersTotal,
        names.arg=WPCGroupR$MembersTotal,
        xlab="Reporter Groups",
        ylab="Total Members",
        legend=WPCGroupR$CoreGroupR,
        col=rainbow(8),
        main="Reporters per Groups",border="red")

barplot(WPCGroupO$MembersTotal,
        names.arg=WPCGroupO$MembersTotal,
        xlab="Owners Groups",
        ylab="Total Members",
        legend=WPCGroupO$CoreGroupO,
        col=rainbow(8),
        main="Owners per Groups",border="red")

```

**3. FINAL CONCLUSIONS:** 

        There are more Reporters than Owners. Maybe because to report a problem in the WorPress Platform is easear than fix a problem. There are a two members who can been consider the super active menbers of WP Community: SergeyBiryukov and johnbillion. SergeyBiryukov (number 1 of owners) was reponsable to 67 tickets, and also he report 15 Tickets (23o position of reporters). johnbillion (number 1 of owners) report 72 tickets, and also was responsable for 16 tickets (3o position of owners). 
        Despite the most of ticket have no owner, there are not so many urgent issues.Thus this seems to be a normal dinamic of the groups. 
        


Owners

##              Var1 Freq
## 6  SergeyBiryukov   67
## 2        audrasjb   18
## 5     johnbillion   16
## 3       chriscct7   15
## 4       joemcgill   14
## 1 adamsilverstein   13

#                Var1 Freq
## 14      johnbillion   72
## 1           afercia   53
## 15  johnjamesjacoby   47
## 29 sebastian.pisula   43
## 9          flixos90   42
## 5   danielbachhuber   39
## 16       karmatosed   33
## 27           rmccue   27
## 31 subrataemfluence   25
## 34      westonruter   24
## 21            nacin   23
## 7           desrosj   22
## 10  garrett-eclipse   22
## 22           pbiron   22
## 3            azaozz   21
## 6              dd32   21
## 4      boonebgorges   19
## 23            pento   17
## 26            ramiy   17
## 28           scribu   17
## 2           anevins   16
## 8          dshanske   15
## 11            helen   15
## 13          iseulde   15
## 18      markjaquith   15
## 19        melchoyce   15
## 30   SergeyBiryukov   15
## 32       swissspidy   15
## 33        tazotodua   15
## 25        Presskopp   14
## 12     henry.wright   13
## 17           mark-k   12
## 20         mukesh27   12
## 24    peterwilsoncc   11

```{r}

# Kendal
cor(WPCGroupO$MembersTotal, WPCGroupR$MembersTotal, method = "kendall")
cor.test(WPCGroupO$MembersTotal, WPCGroupR$MembersTotal, method = "kendall")

```
