---
title: "Machine Learning"
author: "Viviane Schneider"
date: "10/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Machine Learning

Prediction study design

In sample and out of sample errors

Overfitting

Receiver Operating Characteristic (ROC) curves

The caret package in R

Preprocessing and feature creation

Prediction with regression

Prediction with decision trees

Prediction with random forests

Boosting

Prediction blending

https://www.quora.com/Machine-Learning/How-do-I-learn-machine-learning-1

https://www.sciencemag.org/site/feature/data/compsci/machine_learning.xhtml

https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-867-machine-learning-fall-2006/lecture-notes/

http://www.stat.cmu.edu/~cshalizi/350/

https://www.kaggle.com/

https://www.google.org/flutrends/about/
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
