---
title: "WordPress Agents Exploratory Analysis - Part II"
author: "Viviane Schneider"
date: "07/29/2019"
output: html_document
---
**Type of Analysis:** Descriptive analysis - Bivariate description

**Source:** Data come from WordPress Report Trac System.
[URL Source](https://core.trac.wordpress.org/query?status=accepted&status=assigned&status=new&status=reopened&status=reviewing&col=id&col=summary&col=status&col=owner&col=type&col=priority&col=milestone&col=component&col=version&col=severity&col=resolution&col=time&col=changetime&col=focuses&col=reporter&col=keywords&order=priority)
**Dataframe:** [GitHub Repository](https://raw.githubusercontent.com/vivianesch/CoherenceAnalysisWordPress/master/TicketW.csv)

**Date collection:** 04/07/2019.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1. EXPLORATORY ANALYSIS -BIVARIABLE ANALYSIS** 

```{r}
#Install
install.packages("dplyr")
install.packages("SnowballC") # for text stemming
install.packages("wordcloud") # word-cloud generator 
install.packages("RColorBrewer") # color palettes

#Load
library(readr)
library(dplyr)
library(plotly)
library(ggplot2)
library(tidyr)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(data.table)

#READ DATA
TicketW <- read_csv('~/PhD Analysis/1. PhD escriptive exploratory analysis/TicketW.csv')
View(TicketW) # Read 
glimpse(TicketW)

```

**1 REPORTERS AND KEYWORDS ANALYSIS:** Reporters are WordPress Community members who find and report a problem from WP Platform, into a Ticket.

**Goal:** Identify the most frequent used to each report member groups (actives, medians, and aliens).

```{r}

#Import Data
TicketW <- read_csv('~/PhD Analysis/1. PhD escriptive exploratory analysis/TicketW.csv')
View(TicketW) # Read 
glimpse(TicketW)


#Bivariable analysis

#Functions
    #Function .List.f.filter() make variable set that will be filtered
    .List.f.filter = function(x){
        nr<-nrow(x)#Quantity of members
          y<-x[1:nr,1:1] #Select array of members names to filter 
            z<-as.character(y) #Transform names into caracter array
    return(z)
    }
    
    # Function .List.w.Group() Select two key valiables for each group and return a list of inter-ralation of it
    # Where:  x is dataframe with 2 colunms of variables
    # y is a variable yo want to extract a list in order to filter a group
    # f is a list of the group achieve from Function .List.f.filter()
    # i is the main variable you want to show in graphics
    .Top.15.Group = function(x,y,f,i){
        z = subset(x, y %in% f) 
        z<-table(i,y)
          d<-dim(z)
            w<-rowSums(z[1:d[1],1:d[2]])
            w<-as.data.frame(as.table(w)) # Transform to a data frame
            w<- w[order(w$Freq, decreasing = TRUE),] #Ranking
            w<-w[1:15,1:2] #Filter top 10
    return(w)
    } 
    #1.Analyse Keywords used for Active reporters
    Reporter_Keywords<- TicketW %>% select(Reporter,Keywords) #Table of Reporters and Keywords
    summary(Reporter_Keywords)
    dim(Reporter_Keywords)
    glimpse(Reporter_Keywords)
    
#1.1 Analyse Keywords used for Active reporters
    AR<-.List.f.filter(ActiveReporters)
    # 10 top Keywords used by Active Group
Most_Key_AR<-.Top.15.Group(Reporter_Keywords,Reporter_Keywords$Reporter,AR,Reporter_Keywords$Keywords) 
  
 #1.2 Analyse Keywords used for Median reporters
    MR<-.List.f.filter(MedianReporters)
    # 10 top Keywords used by Median Group
Most_Key_MR<-.Top.15.Group(Reporter_Keywords,Reporter_Keywords$Reporter,MR,Reporter_Keywords$Keywords) 
    
#1.3 Analyse Keywords used for Alien reporters
    LR<-.List.f.filter(LessReporters)
    # 10 top Keywords used by Alien Group 
Most_Key_LR<-.Top.15.Group(Reporter_Keywords,Reporter_Keywords$Reporter,LR,Reporter_Keywords$Keywords) 
    

par(mfrow=c(2,3))
    #Graphics of most frequent group words 
    barplot(Most_Key_AR$Freq, las = 2, names.arg = Most_Key_AR$Var1,
            col ="lightblue", main ="Freq. words of Active Reporters",
            ylab = "Word frequencies")
    barplot(Most_Key_MR$Freq, las = 2, names.arg = Most_Key_MR$Var1,
            col ="lightgreen", main ="Freq. words of Median Reporters",
            ylab = "Word frequencies")
    barplot(Most_Key_LR$Freq, las = 2, names.arg = Most_Key_LR$Var1,
            col ="lightgreen", main ="Freq. words of Median Reporters",
            ylab = "Word frequencies")
    
    #Graphics of most frequent group words 
    set.seed(1)
    wordcloud(words = Most_Key_AR$Var1, freq = Most_Key_AR$Freq, min.freq = 1,
              max.words=15, random.order=FALSE, rot.per=0.35, 
              colors=brewer.pal(8, "Dark2"))
    set.seed(1)
    wordcloud(words = Most_Key_MR$Var1, freq = Most_Key_MR$Freq, min.freq = 1,
              max.words=15, random.order=FALSE, rot.per=0.35, 
              colors=brewer.pal(8, "Dark2"))
    set.seed(1)
    wordcloud(words = Most_Key_LR$Var1, freq = Most_Key_LR$Freq, min.freq = 1,
              max.words=15, random.order=FALSE, rot.per=0.35, 
              colors=brewer.pal(8, "Dark2"))





```



